### 2014-02-27 paper/concrete.tex
checkpoint
# Please enter a commit message to explain why this merge is necessary,
# especially if it merges an updated upstream into a topic branch.
#
# Lines starting with '#' will be ignored, and an empty message aborts
# the commit.

The operational semantics we have derived in the previous section
satisfy termination sensitive non-interference by design.  However,
these abstract semantics essentially require that different tasks
execute completely isolated.  For instance, for the mini-ML language,
this means that every task has it's own heap.  For practical
implementations this is often not desirable.  Instead, we would like to
more tightly couple the integration of the target and IFC
language by reusing existing infrastructure.  In the running example,
a concrete implementation might use a single global heap, and ensure
that references do not cross task boundaries, and thus preserving
non-interference.

In this section, we will detail an approach that allows one to implement
a concrete system differently from our proposal in the previous
section, and give conditions for when such a system preserves termination
sensitive non-interference.
We explain the idea for the single heap mini-ML language, and then
generalize to arbitrary systems.

>>>>

The operational semantics we have defined in the previous section
satisfy termination sensitive non-interference by design.
We achieve this general statement that works for a large class of
languages by having different task execute completely isolated from
each other, such that every task has it's own state.
In some cases, this strong separation is desirable, or even necessary.
Languages like C provide direct access to the addresses without
mechanisms in the language to achieve a separation of the heap.
However, for other languages this isolation of tasks can be
undesirable, e.g., for performance reasons.
For instance, for the mini-ML language, our presentation so far
requires a separate heap per task, which is not very practical.
Instead, we would like to
more tightly couple the integration of the target and IFC
language by reusing existing infrastructure.  In the running example,
a concrete implementation might use a single global heap, and ensure
that references do not cross task boundaries, and thus preserving
non-interference.

In this section, we will detail an approach that allows one to implement
a concrete system guided conceptually by the ideas in the previous
section but making different choice for ease of implementation or
performance, and give conditions for when such a system preserves
non-interference.
We first explain the idea for the single heap mini-ML language, and then
generalize to arbitrary languages.
